Simulation of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL

### 2015-01-14 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago Fire: update tex and add files for firetech submission

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof

\input{../../../Bibliography/commoncommands}
\usepackage{graphicx}
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

@@

\title{Simulation of an Attic Firein a Wood Frame Residential Structure - Chicago, IL}

@@

\begin{figure}[!ht]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
\includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
\end{tabular*}
\caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure. Stairs and key rooms are identified using measurements collected by NIST.}
\label{fig:simp_geom}
\end{figure}

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
   \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
\end{tabular*}
\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
\label{fig:alpha_ex}
\end{figure}

@@

\begin{table}
\centering
\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
\begin{tabular}{cccll}
\toprule[1.5pt]
Baseline    &  Alternative  &  Ventilation  &  Type         &  Side of         \\
Simulation  &  Simulation   &  Area         &               &  Structure       \\
{[s]}       &  {[s]}        &  [m$^2$]      &               &                  \\
\midrule
0           &  0            &  0.11         &  Window       &  Rear            \\
40          &  40           &  0.08         &  Breach (x2)  &  Front and Rear  \\
45          &  45           &  0.12         &  Breach       &  Left            \\
55          &  55           &  0.12         &  Breach       &  Rear            \\
130         &  N/A$^*$      &  1.41         &  Door         &  Rear            \\
135         &  N/A$^*$      &  0.2          &  Breach       &  Left            \\
160         &  160          &  0.80         &  Door         &  Interior        \\
\bottomrule[1.25pt]
\end{tabular}\par
\footnotesize
$^*$These ventilation events were not included in the alternative simulation.
\normalsize
\end{table}

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
\end{tabular*}
\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
\label{fig:geom_grid}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
\label{fig:mult_mesh}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
\caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations. The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s).}
\label{fig:hrr}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
\input{../Scripts/colorbar_metric_pres}
\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.}
\label{fig:pres_159s}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
\label{fig:temp_129s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
\label{fig:temp_159s}
\end{figure}

Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. In this figure, the lower temperature bound is set to 25~$^{\circ}$C (77~$^{\circ}$F), and the upper temperature bound is set to 260~$^{\circ}$C (500~$^{\circ}$F); however, these are only limits on the visualized output, and the actual simulated temperatures may exceed the lower or upper bounds. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}. As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.
\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s after interior door failure.}
\label{fig:temp_161s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 15~s after the interior door failure.}
\label{fig:temp_175s}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
\caption{Post-fire image of interior door.}
\label{fig:chicago_doorfold}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
   \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
\end{tabular*}
\caption{Post-experiment images of door failures.}
\label{fig:SC_doorfold}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
\caption{Summary of simulated flow path on the second floor after interior door failure.}
\label{fig:flowpath_1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
\label{fig:temp_top_159}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 5~s after interior door failure.]
{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
\label{fig:temp_top_165}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 60~s after interior door failure.]
{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
\label{fig:temp_top_220}
\end{figure}

@@

\end{document}
% end of file template.tex

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof

\input{../../../Bibliography/commoncommands}
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

@@

\title{Simulation of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL}

@@

\begin{figure}[!ht]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
\includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
\end{tabular*}
\caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure. Stairs and key rooms are identified using measurements collected by NIST}
\label{fig:simp_geom}
\end{figure}

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
   \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
\end{tabular*}
\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident}
\label{fig:alpha_ex}
\end{figure}

@@

\begin{table}[h!]
\centering
\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
\begin{tabular}{cccll}
\toprule[1.5pt]
Baseline    &  Alternative  &  Ventilation  &  Type         &  Side of         \\
Simulation  &  Simulation   &  Area         &               &  Structure       \\
{[s]}       &  {[s]}        &  [m$^2$]      &               &                  \\
\midrule
0           &  0            &  0.11         &  Window       &  Rear            \\
40          &  40           &  0.08         &  Breach (x2)  &  Front and Rear  \\
45          &  45           &  0.12         &  Breach       &  Left            \\
55          &  55           &  0.12         &  Breach       &  Rear            \\
130         &  N/A$^*$      &  1.41         &  Door         &  Rear            \\
135         &  N/A$^*$      &  0.2          &  Breach       &  Left            \\
160         &  160          &  0.80         &  Door         &  Interior        \\
\bottomrule[1.25pt]
\end{tabular}\par
\footnotesize
$^*$These ventilation events were not included in the alternative simulation.
\normalsize
\end{table}

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
\end{tabular*}
\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh}
\label{fig:geom_grid}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
\caption[Front-right side of the structure within the computational domain]{Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft)}
\label{fig:mult_mesh}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
\caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations. The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s)}
\label{fig:hrr}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
\input{../Scripts/colorbar_metric_pres}
\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure}
\label{fig:pres_159s}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s prior to rear door opening}
\label{fig:temp_129s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s prior to interior door failure}
\label{fig:temp_159s}
\end{figure}

Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic. In this figure, the lower temperature bound is set to 25~$^{\circ}$C (77~$^{\circ}$F), and the upper temperature bound is set to 260~$^{\circ}$C (500~$^{\circ}$F); however, these are only limits on the visualized output, and the actual simulated temperatures may exceed the lower or upper bounds. High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor. Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}. As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door). Note that the conditions in the attic do not appear to change.
\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 1~s after interior door failure}
\label{fig:temp_161s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{FDS simulated temperature contours, 15~s after the interior door failure}
\label{fig:temp_175s}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
\caption{Post-fire image of interior door}
\label{fig:chicago_doorfold}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
   \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
\end{tabular*}
\caption{Post-experiment images of door failures}
\label{fig:SC_doorfold}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
\caption{Summary of simulated flow path on the second floor after interior door failure}
\label{fig:flowpath_1}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 1~s prior to interior door failure]
{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor}
\label{fig:temp_top_159}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 5~s after interior door failure]
{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor}
\label{fig:temp_top_165}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption[Temperature contours on the second floor, 60~s after interior door failure]
{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor}
\label{fig:temp_top_220}
\end{figure}

@@

\end{document}
